% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{ulem}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=1in, right=1in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
\pagenumbering{gobble}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\Huge{Nahyuk Lee}
\hfill{\it\footnotesize Updated \today}}

% --- Contact information and other items ---

\vspace{0.5cm} 
\begin{flushleft}
\begin{tabular}{lll}
% Line 1: Email, GitHub, office location
\textbf{Email}: nahyuk0113@cau.ac.kr      &
\hspace{0.55in} \textbf{GitHub}: github.com/NahyukLEE \\


% Line 2: Phone number, LinkedIn, citizenship
\textbf{Phone}: (+82) 10-2557-5493   & 
\hspace{0.55in} \textbf{LinkedIn}: linkedin.com/in/nahyuk-lee/   & 
\end{tabular}
\end{flushleft}

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{8pt}

% Set the width of each column
\begin{longtable}{p{1.3in}p{4.8in}}

% --- Section: Research interests ---

\nohyphens{\color{OliveGreen}{Research interests}}
& 3D Computer Vision \\
& \\

% --- Section: Education ---

\color{OliveGreen}{Education} 
& \textbf{Chung-Ang University} \hfill Seoul, Republic of Korea \\ 
& B.S in Computer Science and Engineering \hfill Mar. 2019 -- Present \\
& Mentor : Prof. Junseok Kwon  \\
& {\it GPA : 4.26 / 4.5}\\
& \\

% --- Uncomment the next few lines if you want to include some courses ---
%& \textbf{Selected coursework}
%\begin{itemize}[noitemsep,leftmargin=*]
%\item \underline{Relevant subject 1}: Course 1, Course 2, Course 3, Course 4
%\item \underline{Relevant subject 2}: Course 1, Course 2, Course 3, Course 4
%\end{itemize} \\



% --- Section: Publications ---
\nohyphens{\color{OliveGreen}{Publications}} 

& \textbf{Development of 3D Reconstruction and Object Recognition Model using Video} \\
& \uline{\textbf{Nahyuk Lee}}, Kyungtaek Lee, Youngsup Park, Sanghyun Seo, Taemin Lee  \\
& \textit{Journal of Digital Contents Society, vol.21, no.11, pp.2011-2019} \textbf{(KCI)}\\
& DOI : \href{http://doi.org/10.9728/dcs.2020.21.11.2011}{10.9728/dcs.2020.21.11.2011}
& \\


& \textbf{A Study on the Prediction of Emotion from Image by Time-flow using Color Analysis} \\
& Taemin Lee, \uline{\textbf{Nahyuk Lee}}, Sanghyun Seo, Dongwann Kang \\
& \textit{2020 International Conference on Computational Science and Computational Intelligence (CSCI) IEEE, pp.747-749, Las Vegas, United States, 2020 -- Oral}\\
& DOI : \href{https://doi.org/10.1109/CSCI51800.2020.00141}{10.1109/CSCI51800.2020.00141}
& \\

& \textbf{The Method for Creating Paintings depend on User's Emotion} \\
& Taemin Lee, \uline{\textbf{Nahyuk Lee}}, Sanghyun Seo, Kyunghyun Yoon \\
& \textit{International Conference on Innovation Convergence Technology(ICICT2020), Jeju, Korea, 2020 -- Oral}\\
& \\


% --- Section: Research experience ---

\nohyphens{\color{OliveGreen}{Research experience}} 
& \textbf{Research Intern, Computer Vision Lab @ Korea University} \\
& {\it Mentor: Prof. Sangpil Kim (Dept. of AI)} \hfill Mar. 2021 -- Jun. 2021 \\
& Research event-based 3D computer vision. Study about event based vision.
& \\


& \textbf{Research Intern, Computer Graphics Lab @ Chung-Ang University} \\
& {\it Mentors: Prof. Kyunghyun Yoon \& Sanghyun Seo}  \hfill Dec. 2019 -- Feb. 2021 \\
& Research 3D reconstruction for virtual space, affective computing using Machine-Learning.
& \\

% --- Section: Teaching experience ---

{\color{OliveGreen}{Teaching experience}} 
& \textbf{Teaching Assistant @ Chung-Ang University} \hfill Fall 2020 -- Spring 2021 \\
& GE-52431: Understanding SW Programming for Problem Solving \\
& Instructor: Taemin Lee (Davinci SW Education Institute) \\
& Python language mentoring for course students.\\
& \\


% --- Section: Project experience ---

{\color{OliveGreen}{Project experience}} 
& {\textbf{Immersive Interaction in eXtended Reality Space for Real-world}} \\
& {\textbf{Recognition, Augmentation and Control}} \hfill Dec. 2019 -- Feb. 2021 \\
& {\it Funded by National Research Foundation of Korea (NRF)}  \\
& \\

& {\textbf{Development of AI-based Virtual Space Structure Estimation}} \\
& {\textbf{Technology using Interior Space Point Cloud}} \hfill May. 2020 -- Feb. 2021 \\
& {\it Funded by Korea Electronics Technology Institute (KETI)} \\
& {\it Cooperated with Innosimulation Co., Ltd. } \\
& \\
 
& {\textbf{AI-based Dementia Severity Prediction}} \hfill Jun. 2020 -- Feb. 2021 \\
& {\it Cooperated with Chung-Ang University Hospical (CAUHS)}  \\
& \\

% --- Section: Awards, scholarships, etc. ---
% --- Note: section title is spread over two lines ---

{\color{OliveGreen}{Honors and }} 
& \textbf{16th Kwanjeong Scholarship} \hfill Feb. 2021 -- Present \\
{\color{OliveGreen}{Scholarship}} 
& Received Kwanjeong Scholarship from Kwanjeong Educational Foundation. \\
& {\it Full-tuition \& fees during 2 years of undergraduate studies} \\
\\

& \textbf{Undergraduate Fellowship (Merit-based)} \\
& \setlength{\leftskip}{10pt} 1. Da Vinci Scholarship V \hfill Sping 2019 -- Fall 2019\\
& \setlength{\leftskip}{10pt} {\it Admission with highest distinction, Full-tuition during 1 year of Freshman} \\
& \setlength{\leftskip}{10pt} 2. Faculty Honor Scholarship \hfill Fall 2019 \\
& \setlength{\leftskip}{10pt} {\it Dean's List (1st of All), Full-tuition during 1 semester} \\
& \setlength{\leftskip}{10pt} 3. Department Secondary Honor Scholarship \hfill Spring 2020 -- Fall 2020\\
& \setlength{\leftskip}{10pt} {\it Dean's List (Top 10\%), 30\%-tuition during 1 semester} \\
& \setlength{\leftskip}{10pt} 4. SW Specialization Scholarship \hfill Spring 2020 -- Spring 2021\\
& \setlength{\leftskip}{10pt} {\it Research Fellowship funded by Davinci Software Institute at Chung-Ang Univ.} \\
\\

& \textbf{Award} \\
& \setlength{\leftskip}{10pt} 1. Best Paper Award (2nd Grade), Humanities Research \hfill Jul.2020 \\
& \setlength{\leftskip}{20pt} Institute, Chung-Ang Univ  \\
& \setlength{\leftskip}{10pt} 2. Best Paper Award (Top 10\%), International Next-generation \hfill Jul.2020 \\
& \setlength{\leftskip}{20pt} Convergence technology Association  \\
& \setlength{\leftskip}{10pt} 3. Excellence Award in Project, Innovation Center for \hfill Aug. 2020 \\
& \setlength{\leftskip}{20pt} Engineering Education, Chung-Ang Univ.  \\
& \setlength{\leftskip}{10pt} 4. Best Paper Award, Digital Contents Society \hfill Dec. 2020

\\
% --- Section: Various skills (programming, software, languages, etc.) ---

{\color{OliveGreen}{Skills}} 
& \textbf{Programming}\\
& Proficient in: Python \\
& Familiar with: Java, C++, C \\
& \\

& \textbf{Languages} \\
& Native Speaker in Korean, Proficient in English \\
& \\



% --- Section: Other interests/hobbies ---

\nohyphens{\color{OliveGreen}{Other interests}} & Sports, Music and Cello\\

% --- End of CV! ---

\end{longtable}
\end{document}
